Primate Cognition and the Red Queen Hypothesis

### 2021-05-12 Article/Article.Rmd
Update after rerun biogeobears due to data loss - new download 10kTrees

#Create citation fusion between articles and package (based on toolbox function)
citeR(
bibliographyArticle="C:/Users/robira/Documents/PhD/Meta_analysis/Cognition_metaanalysis/Text/bibliographyarticle.bib",
bibliographyOutput="C:/Users/robira/Documents/PhD/Meta_analysis/Cognition_metaanalysis/Text/bibliographyarticlepackage.bib",
rgeos,
geosphere,
phytools,
geiger,
RPANDA,
caper,
neurobase,
misc3d
)

#Load environments
load("C:/Users/robira/Documents/PhD/Meta_analysis/Meta_analysis_cognition_primates/REnvironmentsData_spatial_primate.RData")
load("C:/Users/robira/Documents/PhD/Meta_analysis/Meta_analysis_cognition_primates/REnvironmentsgeography_traits_biogeobears.RData")

@@

  summaryDataOfInterest <- read_delim(paste("C:/Users/robira/Documents/PhD/Meta_analysis/Cognition_metaanalysis/OutputEvolModel/Data",i,".txt", sep=""), "\t", escape_double = FALSE, trim_ws = TRUE)

@@

We used a block of chronogram trees of the Primates taxon of the 10kTrees project (downloaded on the 28/01/2020, version 3), as well as a consensus tree of 1 000 trees for the subsequent phylogenetic analyses. The trees contain `r length(phylo_init$tip.label)` primate species.

@@

#Import data
summaryDataForPlot <- read_delim("C:/Users/robira/Documents/PhD/Meta_analysis/Cognition_metaanalysis/OutputEvolModel/Dataplot.txt","\t", escape_double = FALSE, trim_ws = TRUE)

#Tree
tree <- read.tree("C:/Users/robira/Documents/PhD/Meta_analysis/Cognition_metaanalysis/Raw_data/Tree/Tree_diet.nex")

>>>>

#Create citation fusion between articles and package (based on toolbox function)
citeR(
bibliographyArticle="C:/Users/robira/Documents/PhD/Meta_analysis/Meta_analysis_cognition_primates/Article/bibliographyarticle.bib",
bibliographyOutput="C:/Users/robira/Documents/PhD/Meta_analysis/Meta_analysis_cognition_primates/Article/bibliographyarticlepackage.bib",
rgeos,
geosphere,
phytools,
geiger,
RPANDA,
caper,
neurobase,
misc3d
)

#Load environments
load("C:/Users/robira/Documents/PhD/Meta_analysis/Meta_analysis_cognition_primates/REnvironments/Data_spatial_primate.RData")
load("C:/Users/robira/Documents/PhD/Meta_analysis/Meta_analysis_cognition_primates/REnvironments/geography_traits_biogeobears.RData")

@@

  summaryDataOfInterest <- read_delim(paste("C:/Users/robira/Documents/PhD/Meta_analysis/Meta_analysis_cognition_primates/OutputEvolModel/Data",i,".txt", sep=""), "\t", escape_double = FALSE, trim_ws = TRUE)

@@

We used a block of chronogram trees of the Primates taxon of the 10kTrees project (downloaded on the 11/05/2021, version 3), as well as a consensus tree of 1 000 trees for the subsequent phylogenetic analyses. The trees contain `r length(phylo_init$tip.label)` primate species.

@@

#Import data
summaryDataForPlot <- read_delim("C:/Users/robira/Documents/PhD/Meta_analysis/Meta_analysis_cognition_primates/OutputEvolModel/Dataplot.txt","\t", escape_double = FALSE, trim_ws = TRUE)

#Tree
tree <- read.tree("C:/Users/robira/Documents/PhD/Meta_analysis/Meta_analysis_cognition_primates/Raw_data/Tree/Tree_diet.nex")
